MHF SCP Experiment Visualisations

### 2024-08-07 minos/outcomes/MHF_SCP_visualisations.Rmd
Improved plots, changed lots of labels and ensured consistent colour scheme across different plots for MHF results

require(tidyverse)
require(ggplot2)

@@

```{r}
scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

@@

```{r "datain", include=False}
generate_df_list <- function(summary, scen.list) {
  df.list <- lapply(scen.list, function(scen) {
    df <- read.csv(file = sprintf('%s/combined_summary_%s.csv', scen, summary))
    df$scen <- scen
    return(df)
  })
  return(df.list)
}

@@

```{r "cost_ratio_functions", include = FALSE}

SF_12_cost_ratio <- function(summary_type, scen_list) {

@@

@@

  plot_data2_logged <- plot_data2_confint %>%
    group_by(year, scen) %>%
    summarise(mean_SF12_to_cost_ratio = log(mean_SF12_to_cost_ratio),
              lower = log(lower),
              upper = log(upper))

  # p1 <- ggplot(plot_data1, aes(x = year, y = diff_SF_12, group = scen, colour = scen, fill = scen)) +
  #   geom_smooth()
  p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed')

@@

  p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p3 <- ggplot(plot_data2_logged, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen, colour = scen, fill = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point()

  print(p1)
  print(p2)
  #print(p3)
}

SF_12_cost_ratio_cumul <- function(summary_type, scen_list) {

@@

  p1 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
    geom_col() +
    labs(title = 'Ratio of SF12 Improvement to Cost') +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

  p2 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio, group = scen, fill = scen)) +
    geom_col() +
    geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge', width = 0.25) +
    labs(title = 'Ratio of SF12 Improvement to Cost') +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

@@

```{r "rel_abs_function", include=FALSE}

@@

@@

  p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = subpop), linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

@@

  p1 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = sex), linetype = 'dashed') +
    geom_hline(yintercept = 0, linetype = 'dashed')

  p2 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Mean SF-12 Change', subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  #print(p1)
  print(p2)
}
```

@@

@@

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_50)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_50)
```

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
```

@@

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.60_100)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.60_100)
```

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.60_100)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.60_100)
```

@@

```{r}
SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_100)
SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_100)
```

```{r}
SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_100)
SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_100)
```

@@

## Families with Children

@@

@@

```{r}
scen.list <- c('baseline', '50UniversalCredit')

UC.rel <- do.call(rbind, generate_df_list('UC_rel_pov', scen.list))
UC.abs <- do.call(rbind, generate_df_list('UC_abs_pov', scen.list))

p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
  geom_line(aes(color = subpop), linetype = 'dashed') +
  geom_hline(yintercept = 0, linetype = 'dashed')

p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
  geom_smooth() +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  labs(title = 'Mean SF-12 Change', subtitle = '50UniversalCredit') +
  xlab('Year') +
  ylab('SF-12 Change')

print(p1)
print(p2)
```

scen.list <- c('baseline', '50UniversalCredit')

UC.rel <- do.call(rbind, generate_df_list('UC_kids_rel_pov', scen.list))
UC.abs <- do.call(rbind, generate_df_list('UC_kids_abs_pov', scen.list))

rel.change <- UC.rel %>%
  filter(universal_credit == 1) %>%
  select(run_id, init_relative_poverty, SF_12, mean_cost, year, scen) %>%
  pivot_wider(names_from = scen,
              values_from = c(SF_12, mean_cost),
              names_sep = '.') %>%
  mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
  rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
  pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
               names_to = c(".value", "scen"),
               names_sep = "\\.") %>%
  filter(scen != 'baseline') %>%
  rename(RelativePoverty = diff_SF_12) %>%
  select(run_id, year, init_relative_poverty, RelativePoverty)

rel.change$init_relative_poverty <- factor(rel.change$init_relative_poverty)

ggplot(rel.change, aes(x = year, y = RelativePoverty, group = init_relative_poverty, color = init_relative_poverty, fill = init_relative_poverty)) +
  geom_smooth()

combined_confint <- rel.change %>%
    group_by(init_relative_poverty, year) %>%
    summarise(n = n(),
              mean_SF12_change = mean(RelativePoverty),
              margin = qt(0.975, df = n - 1) * (sd(RelativePoverty) / sqrt(n)),
              lower = mean_SF12_change - margin,
              upper = mean_SF12_change + margin)

ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = init_relative_poverty, colour = init_relative_poverty, fill = init_relative_poverty)) +
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
  geom_line(aes(color = init_relative_poverty), linetype = 'dashed') +
  geom_hline(yintercept = 0, linetype = 'dashed')

# WHAT DO I WANT THIS PLOT TO SHOW??
# Relative poverty group under intervention vs relative poverty group without intervention
# So I should be filtering for universal credit and children and relative poverty == 1
# then compare between intervention group and baseline

@@

>>>>

library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(stringr)
library(grid)

@@

```{r}
scen.colour.list <- c('baseline', '£10', '£20',
               '£25', '£30',
               '£35', '£40', '£45',
               '£50', '£60', '£70',
               '£80', '£90', '£100')

#colours <- display.brewer.all(length(scen.list.full))
#colours <- colorRampPalette( brewer.pal(11,"Spectral") )(14)
colours <- colorRampPalette( brewer.pal(9,"Set1") )(14)
my_palette <- set_names(colours, scen.colour.list)

scen.list.full <- c('baseline', '10UniversalCredit', '20UniversalCredit',
               '25UniversalCredit', '30UniversalCredit',
               '35UniversalCredit', '40UniversalCredit', '45UniversalCredit',
               '50UniversalCredit', '60UniversalCredit', '70UniversalCredit',
               '80UniversalCredit', '90UniversalCredit', '100UniversalCredit')

@@

```{r "datain", include=FALSE}
generate_df_list <- function(summary, scen.list) {
  df.list <- lapply(scen.list, function(scen) {
    df <- read.csv(file = sprintf('%s/combined_summary_%s.csv', scen, summary))
    df$scen <- scen
    return(df)
  })
  return(df.list)
}

@@

```{r "cost_ratio_functions", include=FALSE}

SF_12_cost_ratio <- function(summary_type, scen_list, palette = my_palette) {

@@

  data <- data %>%
    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))

@@

  # p1 <- ggplot(plot_data1, aes(x = year, y = diff_SF_12, group = scen, colour = scen, fill = scen)) +
  #   geom_smooth()
  p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point(aes(color = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    xlab('Year') +
    ylab('Mean SF-12 Change') +
    theme(
        legend.title = element_blank(),  # Remove the legend title
        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
        legend.text = element_text(size = 8),  # Increase the text size for better readability
        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
    ) +
    guides(
        color = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        ),
        fill = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        )
    )

  # if (length(scen_list) > 5) {
  #   p1 <- ggplot(plot_data1_confint, aes(x = year, y = mean_SF12_change, group = scen)) +
  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
  #     geom_line(aes(color = scen), linetype = 'dashed') +
  #     geom_point(aes(color = scen)) +
  #     scale_color_manual(values = palette) +
  #     scale_fill_manual(values = palette) +
  #     xlab('Year') +
  #     ylab('Mean SF-12 Change') +
  #     theme(legend.title = element_blank(),
  #           legend.position = c(0.2, 0.8),
  #           legend.text = element_text(size=5),
  #           legend.key.size = unit(1, 'cm')) +
  #     guides(fill=guide_legend(ncol=2))
  # }

  #          legend.background = element_rect(fill = "white")

@@

  p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
    geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = scen), linetype = 'dashed') +
    geom_point(aes(color = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    xlab('Year') +
    ylab('Mean SF-12 Change') +
    theme(
        legend.title = element_blank(),  # Remove the legend title
        legend.position = c(0.2, 0.7),  # Position the legend inside the plot
        legend.text = element_text(size = 8),  # Increase the text size for better readability
        legend.key.size = unit(0.8, 'cm'),  # Reduce the key size to fit more entries
        legend.spacing.y = unit(0.1, 'cm')  # Add vertical space between legend items
    ) +
    guides(
        color = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        ),
        fill = guide_legend(
            ncol = ifelse(length(unique(plot_data1_confint$scen)) > 5, 2, 1)  # Use 2 columns if more than 5 groups
        )
    )

  # if (length(scen_list) > 5) {
  #   p2 <- ggplot(plot_data2_confint, aes(x = year, y = mean_SF12_to_cost_ratio, group = scen)) +
  #     geom_ribbon(aes(ymin = lower, ymax = upper, color = scen, fill = scen), linetype = 'dotted', alpha = 0.3) +
  #     geom_line(aes(color = scen), linetype = 'dashed') +
  #     geom_point(aes(color = scen)) +
  #     scale_color_manual(values = palette) +
  #     scale_fill_manual(values = palette) +
  #     xlab('Year') +
  #     ylab('Mean SF-12 Change') +
  #     theme(legend.title = element_blank(),
  #           legend.position = c(0.2, 0.8),
  #           legend.text = element_text(size=5),
  #           legend.key.size = unit(1, 'cm')) +
  #     guides(fill=guide_legend(ncol=2))
  # }

SF_12_cost_ratio_cumul <- function(summary_type, scen_list, palette = my_palette) {

@@

  p1 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio)) +
    geom_col(aes(color = scen, fill = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

  p2 <- ggplot(cumulative_SF12_ratio_confint, aes(x = scen, y = mean_SF12_to_cost_ratio)) +
    geom_col(aes(color = scen, fill = scen)) +
    scale_color_manual(values = palette) +
    scale_fill_manual(values = palette) +
    geom_errorbar(aes(ymin = lower, ymax = upper), position = 'dodge', width = 0.25) +
    xlab('Intervention') +
    ylab('Ratio') +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          legend.position = 'none')

@@

```{r "rel_abs_functions", include=FALSE}

@@

  UC.rel <- UC.rel %>%
    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))

  UC.abs <- UC.abs %>%
    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))

  rel.change <- UC.rel %>%
    filter(universal_credit == 1,
           relative_poverty == 1) %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    rename(RelativePoverty = diff_SF_12) %>%
    select(run_id, year, RelativePoverty)

  abs.change <- UC.abs %>%
    filter(universal_credit == 1,
           absolute_poverty == 1) %>%
    select(run_id, SF_12, mean_cost, year, scen) %>%
    pivot_wider(names_from = scen,
                values_from = c(SF_12, mean_cost),
                names_sep = '.') %>%
    mutate(across(starts_with("SF_12"), ~ . - SF_12.baseline)) %>%
    rename_with(~ paste0("diff_", .), starts_with("SF_12")) %>%
    pivot_longer(cols = starts_with("diff") | starts_with("mean_cost"),
                 names_to = c(".value", "scen"),
                 names_sep = "\\.") %>%
    filter(scen != 'baseline') %>%
    rename(AbsolutePoverty = diff_SF_12) %>%
    select(run_id, year, AbsolutePoverty)

  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
  comparison_scen <- paste0("£", comparison_scen)

  p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = subpop), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') + 
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('Mean SF-12 Change')

  p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('Mean SF-12 Change')

compare_init_relative_absolute <- function(comparison_scen, kids = FALSE) {

  if (kids) {
    UC.rel <- do.call(rbind, generate_df_list('UC_kids_init_rel_pov', scen.list))
    UC.abs <- do.call(rbind, generate_df_list('UC_kids_init_abs_pov', scen.list))
  } else {
    UC.rel <- do.call(rbind, generate_df_list('UC_init_rel_pov', scen.list))
    UC.abs <- do.call(rbind, generate_df_list('UC_init_abs_pov', scen.list))
  }

  UC.rel <- UC.rel %>%
    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))

  UC.abs <- UC.abs %>%
    mutate_at("scen", str_replace, "UniversalCredit", "") %>%
    mutate(scen = if_else(scen == "baseline", scen, paste0("£", scen)))

@@

  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
  comparison_scen <- paste0("£", comparison_scen)

  p1 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = subpop), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('Mean SF-12 Change')

  p2 <- ggplot(combined_confint, aes(x = year, y = mean_SF12_change, group = subpop, colour = subpop, fill = subpop)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('Mean SF-12 Change')

@@

  comparison_scen <- gsub("[a-zA-Z ]", "", comparison_scen)
  comparison_scen <- paste0("£", comparison_scen)

  p1 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 'dotted', alpha = 0.3) +
    geom_line(aes(color = sex), linetype = 'dashed') +
    geom_point() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    scale_fill_manual(values = c("#E69F00", "#56B4E9")) +
    scale_color_manual(values = c("#E69F00", "#56B4E9")) +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  p2 <- ggplot(data = gender.confint, aes(x = year, y = mean_SF12_change, group = sex, colour = sex, fill = sex)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(subtitle = comparison_scen) +
    xlab('Year') +
    ylab('SF-12 Change')

  print(p1)
  #print(p2)
}
```

@@

## Cost Ratio: £25 - £50

```{r}
SF_12_cost_ratio(summary_type = 'UC', scen_list = scen.list.25_50)
SF_12_cost_ratio_cumul(summary_type = 'UC', scen_list = scen.list.25_50)
```

@@

@@

@@

@@

### Families with Children

@@

## INITIAL Relative and Absolute Poverty

```{r}
compare_init_relative_absolute(comparison_scen = '25UniversalCredit')
compare_init_relative_absolute(comparison_scen = '50UniversalCredit')
compare_init_relative_absolute(comparison_scen = '70UniversalCredit')
compare_init_relative_absolute(comparison_scen = '100UniversalCredit')
```

### Families with Children

```{r}
compare_init_relative_absolute(comparison_scen = '25UniversalCredit', kids=TRUE)
compare_init_relative_absolute(comparison_scen = '50UniversalCredit', kids=TRUE)
compare_init_relative_absolute(comparison_scen = '70UniversalCredit', kids=TRUE)
compare_init_relative_absolute(comparison_scen = '100UniversalCredit', kids=TRUE)
```

@@

@@

# OLD OR UNWANTED

```{r}
# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_50)
# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_50)
```

```{r}
# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_50)
# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_50)
```

```{r}
# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.60_100)
# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.60_100)
```

```{r}
# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.60_100)
# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.60_100)
```

```{r}
# SF_12_cost_ratio(summary_type = 'whole_pop', scen_list = scen.list.10_100)
# SF_12_cost_ratio_cumul(summary_type = 'whole_pop', scen_list = scen.list.10_100)
```

```{r}
# SF_12_cost_ratio(summary_type = 'families', scen_list = scen.list.10_100)
# SF_12_cost_ratio_cumul(summary_type = 'families', scen_list = scen.list.10_100)
```
